SPARQL on the Open, Decentralised Web

### 2016-06-21 dissertation/index.tex
Add a stub conclusions #9
Use the uiophd class
use UK ENglish
Capitalisation; thanks Helen
Add the papers

\documentclass[a4paper, 12pt, draft]{report}
\usepackage{graphicx}
\usepackage[utf8]{inputenc}
\usepackage{multirow}
%\usepackage{times}
\usepackage{listings}
\usepackage{supertabular}
\usepackage{cite}
\usepackage{amsthm}
\usepackage{tikz}
\usepackage[obeyDraft]{todonotes}
\newcommand*\circled[1]{\tikz[baseline=(char.base)]{
            \node[shape=circle,draw,inner sep=2pt] (char) {#1};}}

@@

\begin{document}
\title{SPARQL on the open, decentralised Web}
\author{Kjetil Kjernsmo}
%\institute{Department of Informatics,
%Postboks 1080 Blindern,
%0316 Oslo, Norway}

@@

\maketitle

@@

\input{introdefhistory}
\input{motivation}
\input{related}
\input{problems}
\input{papersincontext}
\input{cache-proxy}

@@

\end{document}

>>>>

\documentclass[a4paper, 12pt]{uiophd}
\usepackage{graphicx}
\usepackage[utf8]{inputenc}
\usepackage{multirow}
\usepackage{listings}
\usepackage{supertabular}
\usepackage{cite}
\usepackage{amsthm}
\usepackage{tikz}
\usepackage{pdfpages}
\usepackage[obeyDraft]{todonotes}
\newcommand*\circled[1]{\tikz[baseline=(char.base)]{
            \node[shape=circle,draw,inner sep=2pt] (char) {#1};}}

@@

\begin{document}
\title{SPARQL on the Open, Decentralised Web}
\author{Kjetil Kjernsmo}
%\institute{Department of Informatics,
%Postboks 1080 Blindern,
%0316 Oslo, Norway}

@@

\frontmatter
\maketitle

@@

\input{introdefhistory}
\input{motivation}
\input{related}
\input{problems}
\input{papersincontext}
\input{conclusions}
\input{cache-proxy}

@@

\chapter{Papers}

\includepdf[pages=1-last,openright]{/home/kjetil/uio/www_docs/2012/hypermedia-rdf.pdf}
\includepdf[pages=1-last,openright]{/home/kjetil/uio/www_docs/2013/iswc.pdf}
\includepdf[pages=1-last,openright]{paper14.pdf}
\includepdf[pages=1-last,openright]{/home/kjetil/uio/www_docs/2015/cache-survey.pdf}
\includepdf[pages=1-last,openright]{report.pdf}
\includepdf[pages=1-last,openright]{noise.pdf}
\end{document}
